Deliminative verbal reduplication in Mandarin Chinese

### 2024-09-05 replies-reviews.tex

1) Compositionality: this test is not reliable. There are phrases whose meaning is not

compositional (see e.g. kick the bucket, shoot the breeze). Also, take verb-object constructions,
which are ambiguous between words and phrases: e.g. 1:0> dan-xin ‘take on-heart, worry” has a
non-compositional meaning, suggesting that it is a word, but is separable, suggesting that it is a
phrase (see Huang 1984). On p. 14, the author(s) state(s): “The meaning of the reduplication is not
compositional, as it does not mean that the event denoted by the verb happens twice or multiple
times, but rather that the event happens for a short duration and/or for low frequency. This non-
compositionality suggests that a reduplication is more word-like.”

If it were compositional, perhaps the meaning should be something like ‘look look” (do the action twice?) but not multiple times. However, I think it is a matter of iconicity rather than compositionality here. In addition, would this imply that the reduplicated verb is a compound? Its meaning and function, though, seem to be closer to inflection or derivation. If it is a derivational item, i.e. a suffix-like element, it can bear a fix aspectual meaning (delimitative aspect): in this sense, the meaning would be compositional.

2) Lexical integrity: if the reduplicated verb is a word, the position of the perfective aspect
marker le is unexpected. In fact, it is never found in between the two constituents of a compound
word, as the author(s) also show(s) in (27c). Her (2006: 1282), talking about V-4 géi sequences,
states that “The simple fact that the V-gei sequence cannot be separated, as in (19¢) indicates its
lexical integrity”, i.e. they form a single lexical item (745 T fih ji-géi-le ta vs. * 77 T 431 Ji-le géi ta).
\itdopt{St. Mü.: fix brackets and references to examples. The quoted text contains Chinese
  characters. Please try to insert them. Also for the examples below.}

@@

%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\item Pp. 26, lines 24--25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between. [] indicates an underspecified list which could be empty or not''. However, it is not entirely clear what prevents phonological material other than yi and le to appear in between the reduplicated elements. This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.

@@

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% YL
\item
The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level. How can one determine which verbs are exempt from the proposed lexical rule? The proposed rule does not seem to provide a clear prediction of which verbs are allowed and which are excluded from reduplication. Why only some states and achievements are allowed? The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.

%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
As explained above, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
The incompatibility with the progressive aspect marker is explained in the Semantics section.
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
The proposed analysis appears to have a descriptive rather than an explanatory power.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\textbf{Answer:} \itdopt{Stefan, say something. StMü: I would suggest to ignore this comment. }

@@

Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.

%%%%%%%%%%%%%%
\item
p. 20, lines 28--31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
element in the reduplication is the actual verb, which resides under init and proc, and that the
second element is an aspect marker, which resides in the complement position of proc, as it delimits
the process of the event”. Based on my understanding, these authors do not claim that the second
element serves as an aspect marker. They propose that the verb and the reduplicant are the spell-out
of two copies of the same lexical item within the vP domain: the reduplicant is the lower copy, in
complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.

%%%%%%%%%%%%%
\noindent
\textbf{Answer:} We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''

%%%%%%%%%%%%%
\item
p. 32, lines 28--34: “Although these forms are generally considered unacceptable (Li \& Thompson 1981: 30; Hong 1999: 275-276; Basciano \& Melloni 2017: 160; Yang \& Wei 2017: 239), Fan (1964: 269) and Sui (2018: 143) considered AB-yi-AB and AB-le -yi-AB to be possible, even though they both recognized that these two forms are rare.” Given that these patterns were possible in previous stages of the language (see a.0. Basciano \& Melloni 2017), these rare occurrences can be seen as relics of this usage.

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} add a footnote

\itdopt{St.Mü.: Did you add a footnote or is this something to be done?}
%%%%%%%%%%%%%%%%%%%%%%
\end{enumerate}

@@

\section{Reviewer 2}
\begin{enumerate}
\item
This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
clarity and well-organized sections. To enhance clarity, I recommend providing a brief illustration for
technical terms like LTOP, catering to readers less familiar with them.
The authors employ various tests to assert that verb reduplication exhibits more word-like
characteristics than phrase-like, hence justifying its morphological classification. The subsequent
adoption of a Head-Driven Phrase Structure Grammar (HPSG) framework, integrating Minimal
Recursion Semantics (Copestake et al., 2005), presents advantages over prior analyses.
Despite these strengths, certain questions warrant attention. The primary concern revolves around
treating verb reduplication as morphological. The authors compare it with Parallel Verb Compound
(PVC) and Serial Verb Construction (SVC), asserting that verb reduplication aligns more closely with
SVC than PVC in tests like phrase extension, substitution, and conjunction reduction. However, the
choice of SVC over regular verb phrases as a point of comparison with PVC and verb reduplication
lacks clarity. While SVC passes these tests, it is crucial to note that regular verb phrases may not pass
some, e.g., separate modification of subparts within a constituent.
In light of this, concluding that verb reduplication is more word-like and less phrase-like is
questionable, as regular verb phrases encounter similar challenges. Therefore, it is crucial to
explicitly justify why SVC was chosen over regular verb phrases for this comparison. Providing such
clarification will strengthen the robustness of the paper's argumentation and render the conclusion
that verb reduplication should be morphological more convincing.
For additional comments, please refer to the attached PDF file.

\itdopt{St.Mü.: This is the original review. We should say something about it. For example point to
  explanations above or say that the issues will be taken up below when we discuss the reviewers
  detailed comments.}

@@

%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}
\citet{Xie2020} identifies the AABB form as morphological verb reduplication.
Even though we do not agree with \citegen{Xie2020} claim that the distinction between ABAB and AABB lies in the distinction between morphology and syntax,
we do agree that they are different grammatical processes and thus requires separate analyses (See also \citealt[Sec. 4.3]{Deng2013}, \citealt{Wang2023}).
Also note that there are numerous scholars that do consider the forms analyzed here as morphological processes (\citealt[Ch. 4]{Chao1968}, \citealt[Ch. 3]{LiThompson1981}, \citealt[4--5]{Liao2014} and \citealt[Sec. 4]{Sui2018}).
\citet[14--15]{Zhang2000} argues that the AABB form of reduplication develops from a completely separate historical origin from the AA and ABAB forms,
as the former has a intensifying rather than delimitative meaning.
\citet[83--84]{Xie2020} further points out that AABB is much less productive than ABAB.
This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
This is probably the case for those AABBs that have an idiomatic meaning, such as \obj{zhi2-zhi3-dian2-dian3} `point-point-gesture-gesture, gossip'.
%Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
%i.e. monosyllabic verbs are reduplicated separately (as AA and BB respectively) and then compounded together to form AABB.
%This is in line with the proposal in \citet[Sec. 4.2]{Wang2023},
%and also explains why some AABBs do not have a base AB form, such as \textit{zou-zou-ting-ting} `walk-walk-stop-stop, walk for a while and rest for a while', *\textit{zou-ting} `walk-stop'
The current analysis has a broad scope in that it explains all forms of delimitative verbal reduplication, which previous analyses were not able to do.
An analysis for the AABB form of reduplication has to be left for further research.

\itdopt{St. Mü: Können wir das nicht auch AABB? Das ist gar nicht schwer. Ich habe das für
  adverbiale Adjektive bereits implementiert. Man muss nur PHON in zwei Teile \ibox{1} und \ibox{2}
  spalten und dann eben \ibox{1} $\oplus$ \ibox{1} $\oplus$ \ibox{2} $\oplus$ \ibox{2} als PHON-Wert
nehmen. Wenn das wichtig ist, können wir das noch machen. Oder wir machen eine Fußnote hin.}

@@

The key consideration here is that the unacceptability of (26b) and examples such as (2) may not hinge solely on whether part of it can be modified. Instead, it could be associated with the post-verbal placement of the adverb.

Consequently, it becomes challenging to use these examples as support for the argument that verb reduplication should be classified as a morphological rather than a syntactic phenomenon. This is because even regular verb phrases cannot be partially modified in the same manner.

%\textbf{Answer:} %Yes, this is true.

Examples (27) and (28) serve as illustrations to demonstrate the application of the ``Lexical Integrity Hypothesis'' in distinguishing PVC from SVC.

@@

In Section 2.4, the authors asserted that verb reduplication is more phrase-like than word-like based on its similarities with Parallel Verb Compounds as apposed to Serial Verb Construction (SVC).

However, it is crucial to acknowledge that SVC has distinctive features, some of which diverge from those of a standard verb phrase. This raises a concern that a verb phrase might not successfully pass certain tests applicable to SVC, such as the ability for a constituent to be partially modified (A regular verb phrase like 'Verb + Object' cannot be partially modified by an adverb, while each verb in an SVC structure can be modified separately (28)). Therefore, when verb reduplication cannot be partially modified, asserting that it is less phrase-like solely on the basis of its differences from SVC might be inappropriate. This is because even a regular verb phrase faces limitations.

In light of this, it becomes essential to clarify why SVC, rather than regular verb phrases, was
chosen as a comparison to Parallel Verb Compounds. Such clarification would enhance the
persuasiveness of the tests presented in this section.

%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} See above.

\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

@@

\textbf{Answer:} The examples are shortened to improve readability.

\item 
In Page 7 (section 2.3.2), the draft analyzes verbal reduplication with respect to Aktionsarten. Nonetheless, I am not well-aware of the concept. The author(s) might be better to account for the concept first in more detail.

\textbf{Answer:} see above.

\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}

@@

\item
In Page 13,
there is a typo: ... (but see Section 2.3.2). in comparison, ...

\textbf{Answer:} fixed.

\item
In the middle, the draft mentions the -bar derivation and be-prefixation in German. I understand the phenomenon has a similarity to verbal reduplication in Chinese. Yet, at a glance the German examples looked out-of-the-blue to me.

\textbf{Answer:} The German examples are used to illustrate the arguments that morphological processes can be productive and does not necessarily change the category or valency of the input.
To improve readability, English examples are used instead now.

@@

\item
The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
Duanmu (1998) and Schäfer (2009) proposed the following four tests to distinguish words from phrases
in Mandarin Chinese: semantic compositionality, phrasal extension, phrasal substitution and
conjunction reduction.

\textbf{Answer:} See above.

\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to
  exactly. For example: See the answers to Reviewer X, point Y on page Z. If you did something in
  the text to react, say so. This pleases reviewers. They are the kings/queens and want to be take seriously.}

\item
In Page 14, the draft makes use of a new terminology such as ``word-like''. Of course, I can understand the meaning within the context. However, I think the author(s) might be better to use a more academic and formal terminology.

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} reformulate as ``behaves more similar to a word''.

\itdopt{St. Mü.: Was hast Du denn hier gemacht? Das scheint im Text jetzt ganz auskommentiert zu sein.}

@@

%%%%%%%%%%%%%%%%%%%%%%
\item
Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\noindent
\textbf{Answer: }Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.

%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs. Is it what
the author(s) invent only for modeling the verbal reduplication in this drat? If so, the author(s)
want to account more for how it works in AVMs. Otherwise, the author(s) might be better to refer to
the previous analysis about the notion.

\noindent
\textbf{Answer: } We added a footnote on first appearance explaining that the \etag is a more
explicit version of the usual ``\ldots''.

@@

\item
In Section 4, I am expecting the author(s) provide a sample derivation (maybe a tree diagram). The draft provides the subsets about how verbal reduplication can be constrained within the AVMs. On top of them, a full derivation can be made for better understanding.
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

%\itdopt{Stefan. Question to Yanru: Which example should we analyze?}
\noindent
\textbf{Answer: } We added a figure with the analysis of \emph{chang2-le-chang2} and some
accompanying text.

### 2024-09-05 chapters/ch02-Phenomenon.tex
added analysis as unary branching tree, addressed issues pointed out by reviewers

\ex\label{ex:zaichang}%她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
\objex{ta1} \ldots\, \objex{hen4} \objex{xu1yao4} \objex{mu3qin1} \obj{zai4-yi-zai4-chang3} \ldots\\
she {} very need mother be.present-one-be.present-scene\\\jambox{(CCL)}
\glt `She \ldots\, really needs her mother to be present on scene for a little while \ldots'
\z
\footnotetext{\url{https://www.163.com/dy/article/FS1FKUC30534DZO1.html} (Accessed 26th  March 2024).}

@@

%%%%%%%%%%%%
\subsection{Word vs. phrase}\label{sec:word}

>>>>

\ex\label{ex:zaichang}%她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
\gll \objex{ta1} \ldots\, \objex{hen4} \objex{xu1yao4} \objex{mu3qin1} \obj{zai4-yi-zai4-chang3}~\ldots\\
she {} very need mother be.present-one-be.present-scene\\\jambox{(CCL)}
\glt `She \ldots\, really needs her mother to be present on scene for a little while \ldots'
\z
\footnotetext{\url{https://www.163.com/dy/article/FS1FKUC30534DZO1.html} (Accessed 26th  March 2024).}

@@

%%%%%%%%%%%%
\subsection{Word vs.\ phrase}\label{sec:word}

### 2024-09-05 chapters/ch05-Analysis.tex
added analysis as unary branching tree, addressed issues pointed out by reviewers

Like \citet{FanSongBond2015}, we assume lexical rules for reduplication. Our lexical rules are
organized in an inheritance network. \textit{verbal-reduplication-lr} is the most general type for
reduplication lexical rules in this network and the implicational constraint in (\ref{avm:redup}) shows the constraints on all
structures of type \textit{verbal-reduplication-lr}. Such structures take a verb as
\textsc{lexical-daughter (lex-dtr)}.  The output reduplicates the \textsc{phonology (phon)} of the
input verb with the possibility to have further phonological material in between.  \etag{} indicates
an underspecified list which could be empty or not.  A delimitative relation is appended to the
\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb as
argument.  The label of the output \iboxb{2} is identified with the label of the input and with the
label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
relations can be added at the beginning of the \textsc{rels} list to allow for the additional
perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A.  The combination with the
perfective will be elaborated on in the following paragraphs.

@@

\ea\label{avm:pfv-redup}
Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
constraints inherited from \type{perfective-lr} and \type{verbal-reduplication-lr}:
%\resizebox{\linewidth}{!}{
 %   \scalebox{.9}{%
        \avm{
            [\type*{perfective-reduplication-lr}\\
            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
            \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
            rels & <[\type*{perfective-rel}\\
            lbl & \2\\
            arg0 & \3\\
            arg1 & \4]>
            $\oplus$ \5 $\oplus$
            <[\type*{delimitative-rel}\\
            lbl  & \4\\
            arg0 & \3]>\\
            lex-dtr & [phon & \1\\
            synsem\textbar loc & [cat  & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]\\
            rels & \5]
            ]
    }
%}
    %}
\z
For example %(\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as
 (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
\ea\label{ex-he-tasted-the-soup-a-little-bit2}
    \gll \objex{ta1} \obj{chang2}-\obj{le}-\obj{chang2} \objex{tang1}.\\
    he taste-\textsc{pfv}-taste soup\\
    \glt `He tasted the soup a little bit.'
 \z
\ea\label{ex:mrs-soup}
h1 \sliste{ h1:perfective(e1,h2), h2:taste(e1,he,soup), h2:delimitative(e1) }
\z
So the delimitative relation is treated as an adjunct to the main relation of the verb, 
and the perfective relation scopes over both the main relation and the delimitative relation.

@@

\ea\label{avm:AleA}
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
\ea    %\scalebox{.9}{%
        \type{a-le-yi-a-lr} \impl\\
        \avm{
            [%\type*{a-le-yi-a-lr}\\
            phon & \1 \+ \phonliste{ le, yi } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }
%}%&
\ex   % \scalebox{.9}{%
    \type{a-le-a-lr} \impl\\
        \avm{
            [%\type*{a-le-a-lr}\\
            phon & \1 \+ \phonliste{ le } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }
%}
%\end{tabular}
\z
\z

>>>>

Like \citet{FanSongBond2015}, we assume lexical rules for reduplication. Our lexical rules are
organized in an inheritance network. \textit{verbal-reduplication-lr} is the most general type for
reduplication lexical rules in this network and the implicational constraint in (\ref{avm:redup}) shows the constraints on all
structures of type \textit{verbal-reduplication-lr}. Such structures take a verb as
\textsc{lexical-daughter (lex-dtr)}.  The output reduplicates the \textsc{phonology (phon)} of the
input verb with the possibility to have further phonological material in between.  \etag{} indicates
an underspecified list which could be empty or not.\footnote{%
The \etag is equivalent to a tag with a number with the difference that \etag is never shared. We
follow Müller (\citeyear[161]{Mueller2002b}, \citeyear[294]{Mueller2003e}) and elsewhere in using this
notation, since we think this is more
precise than simply using three dots.}
A delimitative relation is appended to the
\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb \iboxb{3} as
argument. The list of relations contains so-called elementary predications. There is no complicated
embedding of relations. Instead each elementary predication comes with a label (\textsc{lbl}). The
label can be used as an argument of another relation or in scope constraints, which are not provided
here to keep things simple. The feature \textsc{ltop} points to the local top. This is the
elementary predication that is considered the top-most one in the \relsl. Other elementary
predications may share the label or have arguments with labels of other elementary predications. We
will discuss an example below when we discuss the perfective lexical rule.
The label of the output \iboxb{2} is identified with the label of the input and with the
label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
relations can be added at the beginning of the \textsc{rels} list to allow for the additional
perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A.  The combination with the
perfective will be elaborated on in the following paragraphs.

@@

\ea\label{avm:pfv-redup}
Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
constraints inherited from \type{perfective-lr} and \type{verbal-redu\-pli\-ca\-tion-lr}:\\
%\resizebox{\linewidth}{!}{
 %   \scalebox{.9}{%
        \avm{
            [\type*{perfective-reduplication-lr}\\
            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
            \punk{synsem\textbar loc\textbar cont\textbar ltop}{ \2}\\ 
            rels & <[\type*{perfective-rel}\\
            lbl & \2\\
            arg0 & \3\\
            arg1 & \4]>
            $\oplus$ \5 $\oplus$
            <[\type*{delimitative-rel}\\
            lbl  & \4\\
            arg0 & \3]>\\
            lex-dtr & [phon & \1\\
            synsem\textbar loc & [cat  & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]\\
            rels & \5]
            ]
    }
%}
    %}
\z
For example %(\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as
 (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
\ea\label{ex-he-tasted-the-soup-a-little-bit2}
    \gll \objex{ta1} \obj{chang2}-\obj{le}-\obj{chang2} \objex{tang1}.\\
    he taste-\textsc{pfv}-taste soup\\
    \glt `He tasted the soup a little bit.'
 \z
\ea\label{ex:mrs-soup}
h1 \sliste{ h1:perfective(e1,h2), h2:taste(e1,he,soup), h2:delimitative(e1) }
\z
So the delimitative relation is treated as an adjunct to the main relation of the verb, 
and the perfective relation scopes over both the main relation and the delimitative relation.

@@

\ea\label{avm:AleA}
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
\ea    %\scalebox{.9}{%
        \type{a-le-yi-a-lr} \impl\\
        \avm{
            [%\type*{a-le-yi-a-lr}\\
            phon & \1 \+ \phonliste{ le, yi } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }
%}%&
\ex   % \scalebox{.9}{%
\label{avm:a-le-a-lr}
    \type{a-le-a-lr} \impl\\
        \avm{
            [%\type*{a-le-a-lr}\\
            phon & \1 \+ \phonliste{ le } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }
%}
%\end{tabular}
\z
\z

The analysis of (\ref{ex-he-tasted-the-soup-a-little-bit2}) is shown in tree format in
Figure~\ref{fig-he-tasted-the-soup-a-little-bit}. The \textsc{lex-dtr} is the daughter in the tree.
\begin{figure}[htbp]
\centering
\begin{forest}
[        \avm{
            [\type*{a-le-a-lr}\\
            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \1\\
            synsem\textbar loc & [ cat  & [ head  & verb\\
                                            spr   & < NP$_{\6}$ >\\
                                            comps & < NP$_{\7}$ > ]\\
                                   cont & [ ltop & \2\\
                                            ind  & \ibox{3} ]] \\
            rels & <[\type*{perfective-rel}\\
            lbl & \2\\
            arg0 & \3\\
            arg1 & \4]> $\oplus$ \5 $\oplus$
            <[\type*{delimitative-rel}\\
            lbl  & \4\\
            arg0 & \3]> ]
    }
[\avm{ [phon & \1 \phonliste{ chang2 }\\
       synsem\textbar loc & [cat  & [ head  & verb\\
                                      spr   & < NP$_{\6}$ >\\
                                      comps & < NP$_{\7}$ > ]\\
                             cont & [ ltop & \4\\
                                      ind  & \3]]\\
        rels & \5 < [\type{taste}\\
                     lbl  & \4\\
                     arg0 & \3\\
                     arg1 & \6\\
                     arg2 & \7 ] > ]
}]]
\end{forest}

\caption{Analysis of \emph{chang2-le-chang2} taste-\textsc{pfv}-taste `taste the soup a little bit'}\label{fig-he-tasted-the-soup-a-little-bit}
\end{figure}

The figure shows how the lexical item for \emph{chang2} `to taste' is inserted as a daughter into
the \type{a-le-a-lr} lexical rule. The arguments of \emph{chang2} `to taste' are represented within the \spr and
the \compsl (see \citet{GSag2000a-u} for English) and the respective argument NPs are linked to the
arguments of \type{taste}: the subject is \textsc{arg1}, the agent, and the object is \textsc{arg2},
the stimulus. See \citet{DKW2021a} for more on linking. The part of speech of the lexical item
(\type{verb}) and the valence information is carried over from the daughter to the mother
unchanged. The semantic contribution of the daughter verb, the value of \ibox{5}, is inserted into
the \relsl of the mother as it was specified in the constraints on the type
\type{perfective-reduplication-lr} in (\ref{avm:pfv-redup}). The \textsc{phon} value of the mother
is the concatentation of \emph{chang2}, \emph{le} and \emph{chang2}, as specified in the constraint
on \type{a-le-a-lr} in (\ref{avm:a-le-a-lr}). The resulting unit \emph{chang2-le-chang2} then
combines with its object forming a VP. This VP is combined with the subject resulting in a complete
verbal projection, a sentence. \emph{chang-le-chang} behaves in the same way as the simple \emph{chang2}.
